---
title: "Calculating evapotranspiration using remotely sensed data"
author: "Pramit Ghosh"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading required packages
```{r}
library(water)
library(readr)
```

## Define Area of Interest (AOI)
```{r}
# Create AOI (625 sq.km. centered on Muenster FHZ weather station)
utm_x = 403490.150
utm_y = 5758499.100
aoi = createAoi(topleft = c(utm_x - 25000, utm_y + 25000), bottomright = c(utm_x + 25000, utm_y - 25000), EPSG = 32632)
```

## Read Weather Station data
```{r}
source("utilities.R")

rain = "data/weather_14-06-2017/Precipitation-data-2021-03-08 12_15_07.csv"
radiation = "data/weather_14-06-2017/Radiation-data-2021-03-08 12_17_32.csv"
humidity = "data/weather_14-06-2017/Relative humidity-data-2021-03-08 12_16_26.csv"
temperature = "data/weather_14-06-2017/Temperature-data-2021-03-08 12_15_39.csv"
wind = "data/weather_14-06-2017/Wind velocity-data-2021-03-08 12_16_05.csv"

weather = read_WS(rain, radiation, humidity, temperature, wind)

weather_time = format(weather$Time, format = "%H:%M:%S")
weather$Time = format(weather$Time, format = "%d/%m/%Y")
weather = cbind(weather_time, weather)
colnames(weather) = c("time", "date", "precipitation", "radiation", "rel_humidity", "temperature", "wind_vel")

```

## Calculate data values at satellite overpass

```{r fig.width=10}
MTLfile = "data/L8_C2/LC08_L1TP_197024_20170614_20200903_02_T1_MTL.txt"
WeatherStation = sat_overpass(L8_L2_MTL = MTLfile, weather = weather, lat = 51.968791, long = 7.59513, elev = 60, height = 2)
```

## Load Landsat 8 Level-2 data
```{r}
source("remove_negatives.R")
L8 = loadImage(path = "data/L8_C2/", sat = "L8", aoi = aoi)
L8 = remove_negatives(L8)
plot(L8)
```

## Load Surface Reflectance data
```{r}
source("loadSR.R")
source("calcAlbedo.R")
L8.SR = loadSR(path = "data/L8_C2/SR/", aoi = aoi)
L8.SR = remove_negatives(L8.SR)
L8.SR = L8_SR(L8.SR)
plot(L8.SR)
```

## Load Digital Elevation Model
```{r fig.width=10}
checkSRTMgrids(L8)
DEM = prepareSRTMdata(path = "data/SRTM_DEM/", extent = L8)
plot(DEM, main = "Digital Elevation Model", legend.args = list(text = 'Elevation (m)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate solar angles
```{r}
surface.model = METRICtopo(DEM)
solar.angles.r = solarAngles(surface.model = surface.model, WeatherStation = WeatherStation, MTLfile)
# plot(solar.angles.r)
```

## Calculate intermediate results

### Calculate incident short-wave radiation
```{r fig.width=10}
Rs.inc = incSWradiation(surface.model = surface.model, solar.angles = solar.angles.r, WeatherStation = WeatherStation)
plot(Rs.inc, main = "Incident short-wave radiation", legend.args = list(text = 'Radiation (W/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

### Calculate Top-of-Atmosphere reflectance
```{r}
image.TOAr = calcTOAr(image.DN = L8, sat = "L8", MTL = MTLfile, incidence.rel = solar.angles.r$incidence.rel, aoi = aoi)
plot(image.TOAr)

# image.SR = calcSR(image.TOAr = image.TOAr, sat = "L7", surface.model = surface.model, incidence.hor = solar.angles.r$incidence.hor, WeatherStation = WeatherStation)
```
### Calculate Albedo
```{r fig.width=10}
# albedo = albedo(image.SR = L8.SR, coeff = "Olmedo", sat = "L8")
# albedo = albedo - 1 #To compensate for too high albedo! (needs more investigation)
albedo = albedo.daSilva(L8.SR)
plot(albedo, main = "Albedo", legend.args = list(text = 'Albedo'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate Leaf Area Index
```{r fig.width=10}
LAI = LAI(method = "metric2010", image = image.TOAr, L = 0.1)
plot(LAI, main = "Leaf Area Index", legend.args = list(text = 'LAI (m^2/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate further intermediate results
```{r}
source("calcLST.R")
```

### Calculate Surface Temperature
```{r fig.width=10}
source("calcLST.R")

L8.ST = loadST(path = "data/L8_C2/SR/", aoi = aoi)
Ts = calcLST(L8.ST)
# Ts = surfaceTemperature(image.DN = L8, LAI = LAI, sat = "L8", WeatherStation = WeatherStation, aoi = aoi, method = "SW")
plot(Ts, main = "Surface Temperature", legend.args = list(text = 'Temperature (K)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

### Calculate incident and outgoing long-wave radiation
```{r fig.width=10}
Rl.out = outLWradiation(LAI = LAI, Ts = Ts)
Rl.inc = incLWradiation(WeatherStation = WeatherStation, DEM = surface.model$DEM, solar.angles = solar.angles.r, Ts = Ts)
plot(Rl.out, main = "Outgoing long-wave radiation", legend.args = list(text = 'Radiation (W/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
plot(Rl.inc, main = "Incoming long-wave radiation", legend.args = list(text = 'Radiation (W/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate Net radiation
```{r fig.width=10}
Rn = netRadiation(LAI, albedo, Rs.inc, Rl.inc, Rl.out)
plot(Rn, main = "Net Radiation", legend.args = list(text = 'Radiation (W/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate Soil Heat Flux
```{r fig.width=10}
G = soilHeatFlux(image = L8.SR, Ts = Ts, albedo = albedo, Rn = Rn, LAI = LAI)
plot(G, main = "Soil Heat Flux", legend.args = list(text = 'Radiation (W/m^2)'), xlab = "Easting (m)", ylab = "Northing (m)")
```

## Calculate Sensible Heat flux
```{r fig.width=10}
source("calcAnchors.R")

Z.om = momentumRoughnessLength(LAI = LAI, mountainous = FALSE, method = "short.crops", surface.model = surface.model)
hot.and.cold = calculate_anchors(image = image.TOAr, Ts, LAI, Rn = Rn, G = G, plots = TRUE, albedo = albedo, Z.om = Z.om, n = 5, anchors.method = "flexible", WeatherStation = WeatherStation, verbose = TRUE)
# hot.and.cold = calcAnchors(image = image.TOAr, Ts, LAI, plots = TRUE, albedo = albedo, Z.om = Z.om, n = 5, anchors.method = "flexible", WeatherStation = WeatherStation, verbose = TRUE)
H = calcH(anchors = hot.and.cold, mountainous = FALSE, Ts = Ts, Z.om = Z.om, WeatherStation = WeatherStation, ETp.coef = 1.05, Z.om.ws = 0.03, DEM = DEM, Rn = Rn, G = G, verbose = TRUE)
```

## Calculate 24h evapotranspiration
```{r fig.width=10}
# Calculate 24h evapotranspiration
ET_WS = dailyET(WeatherStation = WeatherStation, lat = 51.968791, long = 7.59513, elev = 60, height = 2)
ET.24 = ET24h(Rn, G, H$H, Ts, WeatherStation = WeatherStation, ETr.daily = ET_WS)
```

## Validation

### Comparing evapotranspiration for different LULC classes

```{r fig.width=10}
source("validation.R")

leo_coords = c(403873.8,	5759162)
leo_val = val_at_coords(image = ET.24, coord_pair = leo_coords)
print(paste("24 hours ET value calculated at LEO Campus = ", leo_val, " mm/d", sep = ""))

fmo_coords = c(411014.92, 5776294.31)
fmo_val = val_at_coords(image = ET.24, coord_pair = fmo_coords)
print(paste("24 hours ET value calculated at FMO Airport = ", fmo_val, " mm/d", sep = ""))

vpts = read_sf("results/pts.gpkg")
pts_geom = st_geometry(vpts)
ET_pts = lapply(X = pts_geom, FUN = function(x, img) val_at_coords(img, as.numeric(x)), ET.24)
val_results = as.data.frame(cbind(vpts$LULC, as.numeric(unlist(ET_pts))))
val_results$V2 = as.numeric(val_results$V2)
colnames(val_results) = c("LULC", "ET")

boxplot(val_results$ET ~ val_results$LULC, main = "Daily evapotranspiration for different LULC classes", sub = "(20 samples per class)", xlab = "LULC class", ylab = "Evapotranspiration (mm/d)")

```

### Comparison with climate station time-series data

```{r}
ET_results = readRDS("results/ET_results.Rds")
```

```{r eval=FALSE, include=FALSE}
source("ET_func.R")
```

#### At Flughafen Münster/Osnabrück (FMO)

Assuming `ET_results` is present in the environment (after running `ET_func.R`):

```{r fig.width=10}
fmo_coords = c(409569.18, 5776377.16)
ET_FMO = data.frame("Date" = sapply(ET_results, function(img_list){as.character(img_list[[1]])}),
                    "PET_RS" = sapply(ET_results, function(img_list){img_list[[2]]}),
                    "ET_RS" = sapply(ET_results, function(img_list){val_at_coords(img_list[[3]], fmo_coords)}))

FMO_DWD = read_csv("data/weather_FMO/klima_1989-2020_MünsterOsnabrück.csv",
                   col_types = cols(STATIONS_ID = col_skip(),
                                    MESS_DATUM = col_datetime(format = "%Y-%m-%d %H:%M:%S UTC"),
                                    QN_3 = col_skip(), FX.Windspitze = col_skip(),
                                    FM.Windgeschwindigkeit = col_skip(),
                                    QN_4 = col_skip(), RSK.Niederschlagshoehe = col_skip(),
                                    RSKF.Niederschlagsform = col_skip(),
                                    SDK.Sonnenscheindauer = col_skip(),
                                    SHK_TAG.Schneehoehe = col_skip(),
                                    NM.Bedeckungsgrad = col_skip(), VPM.Dampfdruck = col_skip(),
                                    PM.Luftdruck = col_skip(), TMK.Lufttemperatur = col_skip(),
                                    UPM.Relative_Feuchte = col_skip(),
                                    TXK.Lufttemperatur_Max = col_skip(),
                                    TNK.Lufttemperatur_Min = col_skip(),
                                    TGK.Lufttemperatur_5cm_min = col_skip(),
                                    eor = col_skip()))
colnames(FMO_DWD) = c("Date", "ET_DWD")
FMO_DWD$Date = as.character(FMO_DWD$Date)

ET_comparison = merge(x = FMO_DWD, y = ET_FMO, all.y = TRUE)
ET_cor = cor(ET_comparison$ET_DWD, y = ET_comparison$ET_RS)
max_ET = max(ET_comparison$ET_DWD, ET_comparison$PET_RS, ET_comparison$ET_RS)

plot(ET_comparison$ET_DWD, ET_comparison$ET_RS,
     xlab = "Daily ET from Climate station (mm/d)",
     ylab = "Daily ET from Remote Sensing (mm/d)",
     main = "Comparison of daily ET values with climate station data",
     xlim = c(0, max_ET), ylim = c(0, max_ET))
abline(0, 1, col = "Blue", lty = 3)
points(x = ET_comparison$ET_DWD, y = ET_comparison$PET_RS, pch = 4, col = "darkgreen")
legend(x = "topleft", legend = c("Actual ET from remote sensing data", "Potential ET from remote sensing data"), col = c("black", "darkgreen"), pch = c(1,4),
       cex = 0.8, inset = 0.01)

plot(ET_comparison$ET_DWD ~ as.POSIXct(ET_comparison$Date, format = "%Y-%m-%d"), xaxt = "none", ylab = "Evapotranspiration (mm/d)", xlab = "", type = "b", lty = 2, col = "blue", main = "Daily Evapotranspiration at Flughafen Münster/Osnabrück", ylim = c(0, max_ET))
axis(1, at = as.POSIXct(ET_FMO$Date, format = "%Y-%m-%d"), labels = format(as.POSIXct(ET_FMO$Date, format = "%Y-%m-%d"), format = "%m/%Y"), las = 2, cex.axis = 0.8)
title(xlab = "Time", line = 4)
par(new = TRUE)
plot(ET_comparison$ET_RS ~ as.POSIXct(ET_comparison$Date, format = "%Y-%m-%d"), xlab = "", ylab = "", axes = FALSE, type = "b", lty = 2, col = "black")
par(new = TRUE)
plot(ET_comparison$PET_RS ~ as.POSIXct(ET_comparison$Date, format = "%Y-%m-%d"), xlab = "", ylab = "", axes = FALSE, type = "b", lty = 2, col = "darkgreen", pch = 4)
legend(title = "ET calculated using data from", x = "bottomleft", legend = c("Remote Sensing (actual)", "Remote Sensing (potential)", "Climate Station (potential)"), col = c("black", "darkgreen", "blue"), lty = 2, cex = 0.8, inset = 0.01, pch = c(1,4,1), title.adj = 0.1, seg.len = 3)

```

#### At Leonardo Campus, Münster

```{r fig.width=10}
leo_coords = c(403873.8,	5759162)
ET_Leo = data.frame("Date" = sapply(ET_results, function(img_list){as.character(img_list[[1]])}),
                    "PET_RS" = sapply(ET_results, function(img_list){img_list[[2]]}),
                    "ET_RS" = sapply(ET_results, function(img_list){val_at_coords(img_list[[3]], leo_coords)}))
PET_Leo = read_table2("data/ETp_Leo_correctedNA.dat",
                      col_names = FALSE, col_types = cols(X1 = col_date(format = "%m/%d/%Y"),
                                                          X2 = col_time(format = "%H:%M")),
                      skip = 1)
colnames(PET_Leo) = c("Date", "Time", "PET")
Leo_FH = aggregate(x = PET_Leo, by = list(PET_Leo$Date), FUN = mean)[, c("Date", "PET")]
Leo_FH$Date = as.character(Leo_FH$Date)
Leo_ET_comparison = merge(x = Leo_FH, y = ET_Leo, all.y = TRUE)

Leo_max_ET = max(Leo_ET_comparison$PET, Leo_ET_comparison$PET_RS, Leo_ET_comparison$ET_RS, na.rm = TRUE)

plot(Leo_ET_comparison$PET, Leo_ET_comparison$ET_RS,
     xlab = "Daily ET from Climate station (mm/d)",
     ylab = "Daily ET from Remote Sensing (mm/d)",
     main = "Comparison of daily ET values with climate station data",
     xlim = c(0, Leo_max_ET), ylim = c(0, Leo_max_ET))
abline(0, 1, col = "Blue", lty = 3)
points(x = Leo_ET_comparison$PET, y = Leo_ET_comparison$PET_RS, pch = 4, col = "darkgreen")
legend(x = "topleft", legend = c("Actual ET from remote sensing data", "Potential ET from remote sensing data"), col = c("black", "darkgreen"), pch = c(1,4),
       cex = 0.8, inset = 0.01)

plot(Leo_ET_comparison$PET ~ as.POSIXct(Leo_ET_comparison$Date, format = "%Y-%m-%d"), xaxt = "none", ylab = "Evapotranspiration (mm/d)", xlab = "", type = "b", lty = 2, col = "blue", main = "Daily Evapotranspiration at Leonardo Campus", ylim = c(0, Leo_max_ET))
axis(1, at = as.POSIXct(ET_Leo$Date, format = "%Y-%m-%d"), labels = format(as.POSIXct(ET_Leo$Date, format = "%Y-%m-%d"), format = "%m/%Y"), las = 2, cex.axis = 0.8)
title(xlab = "Time", line = 4)
par(new = TRUE)
plot(Leo_ET_comparison$ET_RS ~ as.POSIXct(Leo_ET_comparison$Date, format = "%Y-%m-%d"), xlab = "", ylab = "", axes = FALSE, type = "b", lty = 2, col = "black")
par(new = TRUE)
plot(Leo_ET_comparison$PET_RS ~ as.POSIXct(Leo_ET_comparison$Date, format = "%Y-%m-%d"), xlab = "", ylab = "", axes = FALSE, type = "b", lty = 2, col = "darkgreen", pch = 4)
legend(title = "ET calculated using data from", x = "bottomleft", legend = c("Remote Sensing (actual)", "Remote Sensing (potential)", "Climate Station (potential)"), col = c("black", "darkgreen", "blue"), lty = 2, cex = 0.8, inset = 0.01, pch = c(1,4,1), title.adj = 0.1, seg.len = 2)
```


