---
title: "Remote Sensing data products"
author: "Pramit Ghosh"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Remote Sensing Data Products

We will look at the following remotely sensed data for Muenster and its surrounding areas. These were obtained from or calculated using data from the LANDSAT 8 and SRTM missions.

* Landsat 8 Digital Numbers
* Landsat 8 Surface Reflectance
* Digital Elevation Model (using SRTM)
* Relative Solar Incidence Angle
* Incident Shortwave Radiation
* Top-of-Atmosphere Reflectance
* Albedo
* Leaf Area Index
* Surface Temperature
* Incident Longwave Radiation
* Outgoing Longwave Radiation
* Net Radiation
* Soil Heat Flux
* Daily Evapotranspiration

```{r calculate, include=FALSE}
library(mapview)
source("../ET_L8.R", chdir = TRUE)
```

## Landsat 8 Digital Numbers

```{r L8, message=FALSE, warning=FALSE}
mapview(L8, alpha = 0.8, maxpixels = 3000000)
```

## Landsat 8 Surface Reflectance

```{r message=FALSE, warning=FALSE}
mapview(L8.SR, alpha = 0.8, maxpixels = 3000000)
```

## Digital Elevation Model (in m)

```{r message=FALSE, warning=FALSE}
mapview(DEM, alpha = 0.8, maxpixels = 3000000)
```

## Relative solar incidence angle (in radians)

```{r message=FALSE, warning=FALSE}
mapview(solar.angles.r[[5]], alpha = 0.8, maxpixels = 3000000)
```

## Incident Shortwave Radiation (in W/m^2)

```{r message=FALSE, warning=FALSE}
mapview(Rs.inc, alpha = 0.8, maxpixels = 3000000)
```

## Top-of-Atmosphere Reflectance

```{r message=FALSE, warning=FALSE}
mapview(image.TOAr, alpha = 0.8, maxpixels = 3000000)
```

## Alebdo

```{r message=FALSE, warning=FALSE}
mapview(albedo, alpha = 0.8, maxpixels = 3000000)
```

## Leaf Area Index (in m^2/m^2)

```{r message=FALSE, warning=FALSE}
mapview(LAI, alpha = 0.8, maxpixels = 3000000)
```

## Surface Temperature (in K)

```{r message=FALSE, warning=FALSE}
mapview(Ts, alpha = 0.8, maxpixels = 3000000)
```

## Incident long-wave radiation (in W/m^2)

```{r message=FALSE, warning=FALSE}
mapview(Rl.inc, alpha = 0.8, maxpixels = 3000000)
```

## Outgoing long-wave radiation (in W/m^2)

```{r message=FALSE, warning=FALSE}
mapview(Rl.out, alpha = 0.8, maxpixels = 3000000)
```

## Net Radiation (in W/m^2)

```{r message=FALSE, warning=FALSE}
mapview(Rn, alpha = 0.8, maxpixels = 3000000)
```

## Soil Heat Flux (in W/m^2)

```{r message=FALSE, warning=FALSE}
mapview(G, alpha = 0.8, maxpixels = 3000000)
```

## Daily evapotranspiration (in mm/d)

```{r message=FALSE, warning=FALSE}
mapview(ET.24, alpha = 0.8, maxpixels = 3000000)
```




